\documentclass[11pt]{article}
\usepackage{amsmath,amssymb,amsthm,hyperref}
\newtheorem{theorem}{Theorem}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\newtheorem{remark}{Remark}
\title{Poisson and Weyl lifts of the Alp\"oge--Fable Keller map\\
and nonunique self-adjoint realizations of a dual transport operator}
\author{Daniel Eric Fredriksen\\
Quantyra Inc.\\
\texttt{https://github.com/Quantyra/jacobian-weyl-quantum-phase-space}}
\date{21 July 2026}

\begin{document}
\maketitle

\begin{abstract}
We study the three-dimensional Keller map \(F\) announced by Alp\"oge (with Fable credited): \(\det DF\equiv -2\) and a three-point collision. Theorem~A restates those finite identities; novelty is Theorems~B--F. The cotangent lift \(\Phi(q,p)=(F(q),J^{-T}p)\) is a polynomial Poisson map and non-injective. Dual fields \(X_j=\sum_k B_{jk}\partial_{q_k}\) commute and are divergence-free (Piola), so \(H_j=-iX_j\) are symmetric on \(C_c^\infty(\mathbb{R}^3)\). We define the induced polynomial Weyl endomorphism \(\psi\). The field \(X_1\) is incomplete via an explicit integral curve. In flow-box coordinates \((a,s,c)=F(q)\) one has \(X_1=\partial_s\) and \(\mathrm{d}q=\tfrac12\,\mathrm{d}a\,\mathrm{d}s\,\mathrm{d}c\). Open forward and backward escape walls yield whole-orbit deficiency vectors in \(\operatorname{Dom}(H^*)\) (transverse cutoffs only; no interior \(s\)-indicators), hence
\[
(n_+,n_-)=(\infty,\infty)
\]
for \(H=-iX_1\). Infinitely many self-adjoint extensions exist; the core algebraic CCR/Poisson data alone do not distinguish among them. No gates, channels, computational advantage, or seed discovery claim. Companion code release \textbf{v0.3.4-submit}.
\end{abstract}

\noindent\textbf{MSC 2020:} 47B25, 81S05, 14R15, 37C10, 53D17.\\
\textbf{Software:} v0.3.4-submit; concept DOI 10.5281/zenodo.21474351.\\
\textbf{Categories (suggested):} math.FA (primary); math-ph, math.SP (secondary).

\paragraph{Errata (prior releases).}
v0.2.2 pair \((0,\infty)\) for \(H\) withdrawn. v0.3.0 interior \(s\)-indicator deficiency proof withdrawn (\(\notin\operatorname{Dom}(H^*)\)). This submission is \textbf{\(H=-iX_1\) only}: we do \emph{not} claim exact deficiency pairs for \(H_0,H_2\), nor a theorem-level dual-flow strong CCR no-go (companion notes only).

\section{Introduction}
On 19--20 July 2026, Levent Alp\"oge announced an explicit polynomial map \(F:\mathbb{C}^3\to\mathbb{C}^3\) with \(\det DF\equiv-2\) and a three-point collision, crediting the system Fable~\cite{Alpoge2026,UlamJacobian}. \textbf{We do not claim discovery of \(F\).} Independent checks and Lean formalizations of the seed identities appeared promptly~\cite{FredriksenLean}.

We ask whether the standard Poisson/CCR lifts of \(F\) select a unique self-adjoint dual transport generator on \(C_c^\infty(\mathbb{R}^3)\). For \(H=-iX_1\) the answer is negative: deficiency indices \((\infty,\infty)\).

\paragraph{Scope.} Theorems A--F below concern the algebra of the lifts and the analytic deficiency theory of \(H=-iX_1\). Remarks on other dual fields or alternative realizations are deferred to companion validation notes and are not claimed as theorems here.

\section{Setup}
Let \(q=(q_0,q_1,q_2)=(x,y,z)\) and
\begin{align*}
F_0&=(1+xy)^3 z + y^2(1+xy)(4+3xy),\\
F_1&=y + 3x(1+xy)^2 z + 3xy^2(4+3xy),\\
F_2&=2x - 3x^2 y - x^3 z.
\end{align*}
Write \(J=DF\) and \(B:=J^{-T}\). Dual fields:
\[
X_j:=\sum_{k=0}^{2} B_{jk}(q)\,\partial_{q_k},\qquad j=0,1,2.
\]
On \(L^2(\mathbb{R}^3)\) set \(p_k=-i\partial_{q_k}\) (\(\hbar=1\)). When \(\operatorname{div} X_j=0\),
\[
H_j:=-iX_j
\]
is symmetric on \(C_c^\infty(\mathbb{R}^3)\). Collision data (char \(\neq 2\)):
\begin{equation}
F\bigl(0,0,-\tfrac14\bigr)
=F\bigl(1,-\tfrac32,\tfrac{13}2\bigr)
=F\bigl(-1,\tfrac32,\tfrac{13}2\bigr)
=\bigl(-\tfrac14,0,0\bigr).
\label{eq:collision}
\end{equation}

\section{Theorem A --- seed identities}
\begin{theorem}[A]
(1) \(\det DF\equiv -2\).
(2) The collision identities \eqref{eq:collision} hold over any field of characteristic not \(2\).
(3) Hence \(F\) is not injective.
\end{theorem}
\begin{proof}
Expand \(\det J\) as a polynomial identity, or evaluate the formal determinant in a computer algebra system; independently formalized in Lean 4 (\(\mathtt{jacobianDet\_F}\), \(\mathtt{evalMap\_F\_p0/p1/p2}\))~\cite{FredriksenLean}. Non-injectivity is immediate from \eqref{eq:collision}.
\end{proof}

\begin{remark}[Complex vs real]
Over \(\mathbb{C}\), constant nonzero Jacobian and non-injectivity would be extraordinary for the Jacobian conjecture. We treat \(F\) as an externally announced seed~\cite{Alpoge2026,UlamJacobian}; Theorem~A is a restatement with independent verification, not a priority claim. Our analytic results use the real \(L^2(\mathbb{R}^3)\) dual-field package.
\end{remark}

\section{Theorem B --- Poisson cotangent lift}
\begin{theorem}[B]
Let \(\Phi(q,p)=(F(q),B(q)p)\) with \(B=J^{-T}\). Then:
\begin{enumerate}
\item \(B\) is polynomial and \(JB^{T}=I\);
\item writing \(Q_i=F_i(q)\) and \(P_j=\sum_k B_{jk}(q)p_k\),
\[
\{Q_i,Q_j\}=0,\quad
\{P_i,P_j\}=0,\quad
\{Q_i,P_j\}=\delta_{ij}
\]
for the canonical Poisson structure on \(T^*\mathbb{R}^3\);
\item \(\Phi\) is not injective (lift the three collision sources with matching \(p\)).
\end{enumerate}
\end{theorem}
\begin{proof}
(1) follows from \(B=J^{-T}\) and \(\det J\equiv-2\neq 0\); polynomiality of \(B\) is the classical adjugate formula \(B=-(\operatorname{adj} J)^{T}/2\).
(2) The identities \(\{Q_i,P_j\}=(JB^{T})_{ij}=\delta_{ij}\) are immediate; vanishing of \(\{Q_i,Q_j\}\) is clear; vanishing of \(\{P_i,P_j\}\) is the standard cotangent-lift calculation for \(B=J^{-T}\) (equivalently dual-CAS generator checks in the companion release~\cite{FredriksenSoft}).
(3) If \(F(q^{(a)})=Q_\star\) and \(p^{(a)}=J(q^{(a)})^{T}P_\star\), then \(\Phi(q^{(a)},p^{(a)})=(Q_\star,P_\star)\) for each collision source in \eqref{eq:collision}.
\end{proof}

\section{Theorem C --- dual fields, Piola, Weyl endomorphism}
\begin{theorem}[C]
\begin{enumerate}
\item \(X_j(F_i)=\delta_{ij}\), \([X_i,X_j]=0\), and \(\operatorname{div} X_j=0\).
\item Each \(H_j=-iX_j\) is symmetric on \(C_c^\infty(\mathbb{R}^3)\), and \([M_{F_i},H_j]=i\delta_{ij}\) on that domain.
\item Let \(\mathcal{W}\) be the polynomial Weyl algebra over \(\mathbb{C}\) generated by \(q_k,p_\ell\) with \([q_i,p_j]=\delta_{ij}\) and all other generators commuting. The assignment
\[
\psi(q_i)=F_i(q),\qquad
\psi(p_j)=\sum_k B_{jk}(q)\,p_k
\]
extends uniquely to a unital algebra endomorphism \(\psi:\mathcal{W}\to\mathcal{W}\) preserving the Weyl relations on generators (ordering: coefficients \(B_{jk}(q)\) to the left of \(p_k\)).
\end{enumerate}
\end{theorem}
\begin{proof}
(1) \(X_j(F_i)=(JB^{T})_{ij}=\delta_{ij}\). Then \([X_i,X_j](F_k)=0\) for all \(k\); since \(\mathrm{d}F\) is a coframe, \([X_i,X_j]=0\). Piola: \(\operatorname{Div}\operatorname{Cof}(DF)=0\); with \(\det DF\equiv-2\), \(\operatorname{Div} B=0\), i.e.\ \(\operatorname{div} X_j=0\).
(2) Divergence-free smooth vector fields give symmetric \(-iX\) on \(C_c^\infty\)~\cite{RS2}; the multiplication commutator is \(iX_j(F_i)\).
(3) Universal property of the Weyl algebra: it suffices to check the images satisfy the same commutation relations, which is the content of the Poisson/CCR generator calculation in Theorem~B (with \(\{,\}\mapsto\frac1i[,]\))~\cite{DixmierWeyl}.
\end{proof}

\begin{remark}
\(\psi\) is \emph{not} claimed to extend to a unitary conjugation on \(L^2\), a \(C^*\) automorphism, or a quantum channel.
\end{remark}

\section{Theorem D --- incompleteness of \(X_1\)}
\begin{theorem}[D]
The dual field \(X_1\) is incomplete on \(\mathbb{R}^3\).
\end{theorem}
\begin{proof}
For \(t\in[0,\tfrac12)\), with continuous extension \(\gamma(0)=(1,0,0)\), set
\begin{align*}
q_0(t)&=\frac{-2t-\sqrt{1-2t}+1}{t(2t-1)},\\
q_1(t)&=t,\\
q_2(t)&=t^2\bigl(2t-3\sqrt{1-2t}-1\bigr)
\end{align*}
on \((0,\tfrac12)\), and \(\gamma(t)=(q_0(t),q_1(t),q_2(t))\). Then \(\gamma\) is \(C^\infty\) on \((0,\tfrac12)\) and extends \(C^1\) to \(t=0\). Computer algebra gives the polynomial/algebraic identity \(F(\gamma(t))=(0,t,2)\) on \((0,\tfrac12)\)~\cite{FredriksenSoft}. Differentiating yields \(DF_{\gamma(t)}\gamma'(t)=e_1\). Since \(DF\cdot X_1=e_1\) uniquely, \(\gamma'=X_1\circ\gamma\).

As \(t=\tfrac12-\varepsilon\) with \(\varepsilon\downarrow 0\),
\[
q_0(t)=\sqrt{2/\varepsilon}+O(1)\to+\infty,
\]
so \(\gamma(t)\) leaves every compact of \(\mathbb{R}^3\) in finite time. Hence \(X_1\) is incomplete.
\end{proof}

\section{Flow-box coordinates}
Along the \(X_1\) flow (where defined), \(X_1 F_0=X_1 F_2=0\) and \(X_1 F_1=1\). On any open set carrying a smooth local inverse of \(F\) (locally everywhere: \(\det DF\equiv-2\neq 0\)), the coordinates \((a,s,c)=F(q)\) satisfy
\begin{equation}
\mathrm{d}q
=\frac{1}{|\det DF|}\,\mathrm{d}a\,\mathrm{d}s\,\mathrm{d}c
=\tfrac12\,\mathrm{d}a\,\mathrm{d}s\,\mathrm{d}c,
\qquad
X_1=\partial_s,
\qquad
H:=-iX_1=-i\partial_s.
\tag{7.1}
\label{eq:flowbox}
\end{equation}
Indeed, if \(\Psi\) is a local inverse sheet, \(D\Psi=(DF)^{-1}\) and
\[
\bigl|\det D\Psi\bigr|
=\frac{1}{|\det DF|}=\tfrac12,
\]
so Lebesgue measure pushes forward with factor \(\tfrac12\) (orientation chosen so the factor is positive).

Eliminating \(q_2\) from \(F_2=c\) and \(q_1\) from \((F_0,F_1)=(a,s)\) yields
\begin{equation}
A(s;a,c)\,q_0^3+B(s;c)\,q_0+C(c)=0,
\tag{7.2}
\label{eq:cubic}
\end{equation}
with
\[
A=-cs^3+s^2+18acs-27a^2c^2-16a,\quad
B=3cs-4,\quad
C=2c.
\]
If \(A\to 0\) with \(B\neq 0\), Vieta forces some \(|q_0|\to\infty\).

\paragraph{Reconstruction.}
If \(x=q_0\neq 0\) solves \eqref{eq:cubic} and the denominators below are nonzero,
\begin{equation}
\begin{aligned}
q_1
&=\frac{9acx^2-3csx-3c-sx^2+6x}{x\bigl((3cs-4)x+3c\bigr)},\\
q_2
&=\frac{2x-3x^2q_1-c}{x^3},
\end{aligned}
\tag{8.0}
\label{eq:recon}
\end{equation}
then \(F(x,q_1,q_2)=(a,s,c)\) by polynomial identity.

\section{Escape walls and deficiency indices}
Write
\[
n_+:=\dim\ker(H^*-i),\qquad
n_-:=\dim\ker(H^*+i).
\]

\subsection{Per-orbit dictionary}
On \(L^2((\ell,r),\mathrm{d}s)\) with \(h=-i\partial_s\) minimal on \(C_c^\infty(\ell,r)\)~\cite{RS2}:
finite upper end \(\Rightarrow\dim\ker(h^*+i)=1\) (model \(e^{s-r}\));
finite lower end \(\Rightarrow\dim\ker(h^*-i)=1\) (model \(e^{-(s-\ell)}\)).

\subsection{Forward wall}
\begin{proposition}[Forward wall]
There exist a nonempty open \(U_+\subset\mathbb{R}^2\) and \(\beta\in C^\infty(U_+)\) such that for every \((a,c)\in U_+\) a selected real inverse branch of \(F\) exists on an \(s\)-interval with finite upper end \(s=\beta(a,c)\) and \(\|q\|\to\infty\) as \(s\to\beta^-\).
\end{proposition}
\begin{proof}
At the base \(p_\star=(a,s,c)=(0,\tfrac12,2)\): \(A(p_\star)=0\), \(A_s:=\partial_s A(p_\star)=-\tfrac12\neq 0\), \(B(p_\star)=-1\neq 0\). By the implicit function theorem there is a neighborhood of \((0,2)\) and \(\beta\in C^\infty\) with \(\beta(0,2)=\tfrac12\) and \(A(\beta(a,c);a,c)=0\).

Set \(\tau=\sqrt{\beta-s}\) and \(q_0=r/\tau\). Define
\[
G_+(a,c,\tau,r)
:=\frac{A(\beta-\tau^2;a,c)}{\tau^2}\,r^3
+B(\beta-\tau^2;c)\,r
+C(c)\,\tau
\quad(\tau\neq 0),
\]
and extend at \(\tau=0\) by
\[
G_+(a,c,0,r)=(-A_s(\beta;a,c))r^3+B(\beta;c)r.
\]
Smoothness of the extension follows from \(A(\beta)=0\) and the Taylor expansion \(A(\beta-\tau^2)=-A_s(\beta)\tau^2+O(\tau^4)\) in \(\tau^2\). At the base, \(G_+(0,2,0,r)=\tfrac12 r^3-r\) has simple roots \(r=\pm\sqrt{2}\) because \(\partial_r G_+=\tfrac32 r^2-1\) and \(\partial_r G_+(\pm\sqrt{2})=-2B=2\neq 0\). The IFT continues \(r_\pm(a,c,\tau)\) on an open set \(U_+\times(0,\tau_0)\). Then \(|q_0|=|r_\pm|/\tau\to\infty\) as \(\tau\downarrow 0\).

For reconstruction, the denominator in \eqref{eq:recon} behaves as \(q_0(Bq_0+3c)\sim B q_0^2\) with \(B\to-1\neq 0\), hence is nonzero for small \(\tau\) after shrinking \(U_+\). The formulas for \(q_1,q_2\) are rational in \((q_0,s,a,c)\) with this nonvanishing denominator; combined with \(q_0\sim r/\tau\) one obtains the spatial escape lower bound
\[
\|q\|\ge |q_0|\ge \frac{c_0}{\sqrt{\beta-s}}
\]
for some \(c_0>0\) on a possibly smaller relatively compact \(W_+\Subset U_+\) and \(s\) near \(\beta\). Regression checks: \texttt{data/anchor/cas\_orbit\_measure\_IFT\_A001.json}~\cite{FredriksenSoft}.
\end{proof}

\subsection{Backward wall}
\begin{proposition}[Backward wall]
There exist a nonempty open \(U_-\) and \(\alpha\in C^\infty(U_-)\) such that for \((a,c)\in U_-\) a selected real branch exists for \(s>\alpha(a,c)\) with \(\|q\|\to\infty\) as \(s\downarrow\alpha^+\).
\end{proposition}
\begin{proof}
At \(a=\tfrac1{54}\), \(c=2\),
\[
A\bigl(s;\tfrac1{54},2\bigr)=-\frac{(2s-1)(3s^2-1)}{3},
\]
so \(A(\tfrac12)=0\), \(A_s(\tfrac12)=\tfrac16>0\), \(B(\tfrac12)=-1\). IFT gives a wall \(\alpha\) near \(\tfrac12\). Set \(\tau=\sqrt{s-\alpha}\) and \(q_0=r/\tau\), and define \(G_-\) analogously, extended at \(\tau=0\) by \(A_s(\alpha)r^3+B(\alpha)r\). At the base, simple roots \(r=\pm\sqrt{6}\) (\(\partial_r G_-=-2B\neq 0\)). IFT yields open \(U_-\) and large-\(q_0\) branches; reconstruct via \eqref{eq:recon}. Escape: \(\|q\|\ge c_0'/\sqrt{s-\alpha}\). Regression: \texttt{cas\_backward\_incomplete\_wall\_A001.json}.
\end{proof}

\subsection{Saturated maximal sheets}
\begin{lemma}[Saturated maximal sheets]
Let \(W_+\Subset U_+\) be nonempty, open, and relatively compact. On the selected large-\(q_0\) forward branch, pick \(\varepsilon_0>0\) small and the smooth cross-section
\[
\Sigma_+=\bigl\{q:F(q)=(a,\beta(a,c)-\varepsilon_0,c),\;(a,c)\in W_+\bigr\}.
\]
Let \(\phi_t\) be the maximal flow of \(X_1\). Because \(X_1 F_1=1\), \(F_1(\phi_t(q))=F_1(q)+t\) on the existence interval. Define
\[
D_+=\bigl\{(a,c,s):(a,c)\in W_+,\;\ell_+(a,c)<s<\beta(a,c)\bigr\},
\]
where \((\ell_+,\beta)\) is the maximal open \(s\)-interval of the selected immersed branch. Then
\[
\Psi_+:D_+\to\Omega_+\subset\mathbb{R}^3,
\qquad
\Psi_+(a,c,s)=\phi_{s-(\beta-\varepsilon_0)}(q_\Sigma(a,c))
\]
is a \(C^\infty\) diffeomorphism onto an open \(X_1\)-invariant set, \(F\circ\Psi_+=(a,s,c)\), and \(s\to\beta^-\) occurs at spatial infinity. If \(\ell_+\) is finite, maximality forces escape as \(s\downarrow\ell_+\) as well. An analogous \(\Psi_-,\Omega_-\) exists for the lower wall.
\end{lemma}
\begin{proof}
The flow domain of a smooth vector field is open and the flow is \(C^\infty\)~\cite{LeeSmooth}. Uniqueness gives injectivity of \(\Psi_+\). Local invertibility of \(F\) and the flowbox theorem imply \(\Omega_+\) is open. The upper end is the wall of the forward-wall proposition, hence not attained in \(\mathbb{R}^3\). Finite lower maximal time forces escape from compacts by standard ODE maximality.
\end{proof}

\subsection{Deficiency vectors in \(\operatorname{Dom}(H^*)\)}
\begin{lemma}[Deficiency vectors]
For \(\chi\in C_c^\infty(W_+)\) define on the entire maximal interval
\[
u_-\bigl(\Psi_+(a,c,s)\bigr)
:=\chi(a,c)\,e^{s-\beta(a,c)},
\]
and \(u_-=0\) off \(\Omega_+\). No interior \(s\)-cutoff. Then \(u_-\in L^2(\mathbb{R}^3)\), \(u_-\in\operatorname{Dom}(H^*)\), and \((H^*+i)u_-=0\). The linear map \(\chi\mapsto u_-\) is injective, so \(n_-=\infty\). Likewise
\[
u_+\bigl(\Psi_-(a,c,s)\bigr)
:=\chi(a,c)\,e^{-(s-\alpha(a,c))}
\]
on \((\alpha,r_-)\) yields \(n_+=\infty\).
\end{lemma}
\begin{proof}
\textit{Square-integrability.} By \eqref{eq:flowbox},
\[
\|u_-\|_2^2
=\tfrac12\int_{W_+}|\chi|^2
\Bigl(\int_{\ell_+}^{\beta}e^{2(s-\beta)}\,\mathrm{d}s\Bigr)
\mathrm{d}a\,\mathrm{d}c
\le\tfrac14\|\chi\|_{L^2(W_+)}^2,
\]
since the inner integral equals \(\tfrac12\bigl(1-e^{2(\ell_+-\beta)}\bigr)\le\tfrac12\).

\textit{Adjoint equation.} Let \(\varphi\in C_c^\infty(\mathbb{R}^3)\). Compact support meets each orbit in a closed bounded \(s\)-segment strictly inside \((\ell_+,\beta)\) whenever it meets \(\Omega_+\) (escape ends lie outside every compact). On \(\Omega_+\), \(H=-i\partial_s\) in the flow-box chart with density \(\tfrac12\), and \(\operatorname{div} X_1=0\), so the formal adjoint of \(-iX_1\) is again \(-iX_1\). Integrating by parts in \(s\) for almost every \((a,c)\) (Fubini) produces no endpoint contributions inside \(\operatorname{supp}\varphi\). There is no interior jump because \(u_-\) has no artificial \(s\)-cutoff. Off \(\Omega_+\), \(u_-=0\). Lateral boundaries of \(W_+\) contribute nothing because \(\chi|_{\partial W_+}=0\), so no transverse surface measure appears in the distributional pairing. Hence
\[
\langle u_-,H\varphi\rangle=\langle -iu_-,\varphi\rangle,
\]
i.e.\ \(u_-\in\operatorname{Dom}(H^*)\) and \((H^*+i)u_-=0\).

\textit{Infinite dimension.} If \(u_-=0\) a.e., then \(\chi=0\) a.e.\ on \(W_+\) because \(\Psi_+\) is a diffeomorphism and the exponential factor never vanishes. Thus \(\chi\mapsto u_-\) embeds an infinite-dimensional space into \(\ker(H^*+i)\).

The lower-wall argument is symmetric.
\end{proof}

\begin{remark}[Withdrawn device]
Interior indicators \(\mathbf{1}_{(\beta-\delta,\beta)}(s)\) create \(\delta\)-masses and exit \(\operatorname{Dom}(H^*)\). That construction is withdrawn.
\end{remark}

\begin{theorem}[F]
\((n_+,n_-)=(\infty,\infty)\).
\end{theorem}
\begin{proof}
Forward and backward walls, saturation, and the deficiency lemma. Separability of \(L^2(\mathbb{R}^3)\) makes both dimensions countably infinite.
\end{proof}

\begin{theorem}[E]
\(H=-iX_1\) is not essentially self-adjoint on \(C_c^\infty(\mathbb{R}^3)\).
\end{theorem}
\begin{proof}
\(n_\pm\ge 1\) by Theorem~F.
\end{proof}

\begin{corollary}
By von Neumann's theorem, infinitely many self-adjoint extensions of \(H\) exist. Every such extension agrees with the same minimal operator on \(C_c^\infty(\mathbb{R}^3)\); the core algebraic Poisson/CCR relations recorded in Theorems~B--C therefore do not, by themselves, distinguish a unique extension.
\end{corollary}

\section{Discussion}
The example separates algebraic and analytic layers. The Poisson cotangent lift and dual-field/CCR identities are clean, and \(\psi\) is a well-defined polynomial Weyl endomorphism. Nonetheless \(X_1\) is incomplete and \(H=-iX_1\) has deficiency indices \((\infty,\infty)\). Algebraic CCR/Poisson data therefore do not select a unique self-adjoint dual momentum for this generator.

We do \emph{not} claim here exact deficiency indices for \(H_0\) or \(H_2\), nor a theorem classifying all strong CCR or dual-translation packages; those topics appear only in companion repository notes and may be incomplete relative to theorem grade.

Classical incomplete flows and half-line models are standard~\cite{RS2}. The contribution is the geometric dual-lift package for this Keller seed together with an explicit two-sided wall construction for \(H=-iX_1\).

\section{Non-claims}
No unitary gate, channel, CP map, or computational advantage. No preferred physical extension. No claim that all quantization routes fail. Discovery of \(F\) not claimed. Lean: seed identities and algebraic dual-matrix packaging only~\cite{FredriksenLean}. No theorem-level dual-flow strong CCR obstruction in this note.

\begin{thebibliography}{99}
\bibitem{RS2}
M.~Reed and B.~Simon, \emph{Methods of Modern Mathematical Physics II: Fourier Analysis, Self-Adjointness}, Academic Press, 1975.

\bibitem{DixmierWeyl}
J.~Dixmier, \emph{Sur les alg\`ebres de Weyl}, Bull.\ Soc.\ Math.\ France \textbf{96} (1968), 209--242.

\bibitem{LeeSmooth}
J.~M.~Lee, \emph{Introduction to Smooth Manifolds}, 2nd ed., Springer, 2013.

\bibitem{BassCW}
H.~Bass, E.~H.~Connell, and D.~Wright, The Jacobian conjecture: reduction of degree and formal expansion of the inverse, Bull.\ Amer.\ Math.\ Soc.\ \textbf{7} (1982), 287--330.

\bibitem{Alpoge2026}
L.~Alp\"oge, announcement of a Keller map with constant Jacobian and collision, July 2026 (credits Fable); see also~\cite{UlamJacobian}.

\bibitem{UlamJacobian}
Ulam / related public write-ups of the July 2026 Jacobian counterexample announcement (seed provenance for \(F\)); archived snapshots and collision data in the companion repository~\cite{FredriksenSoft}.

\bibitem{FredriksenSoft}
D.~E.~Fredriksen, EXOTIC-CCR A001 companion code and CAS certificates, GitHub \texttt{Quantyra/jacobian-weyl-quantum-phase-space}, release \texttt{v0.3.4-submit}, concept DOI 10.5281/zenodo.21474351.

\bibitem{FredriksenLean}
D.~E.~Fredriksen, \texttt{exotic-ccr-lean}, GitHub \texttt{Quantyra/exotic-ccr-lean} (Lean 4 seed and dual-matrix algebra).
\end{thebibliography}
\end{document}
